---
title: "MRMCaov: Multi-Reader Multi-Case Analysis of Variance"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

**MRMCaov** is an R package for statistical comparison of diagnostic tests - such as those based on medical imaging - for which ratings have been obtained from multiple readers and on multiple cases.  Features of the package include the following.

* Comparison of imaging modalities or diagnostic tests with respect to ROC metrics
* ROC metrics include AUC, partial AUC, sensitivity, and specificity as well as user-defined metrics
* Parametric and nonparametric estimation and plotting of ROC curves
* Support for factorial and nested study designs
* DeLong, jackknife, and unbiased covariance estimation
* Inference for random or fixed readers and cases
* Compatibility with Microsoft Windows, Mac OS, and Linux


## Download and Installation

To install the package, do the following:

1. Download the archive file for your operating system from the links provided in the table below.
2. Run [RStudio](https://www.rstudio.com/products/rstudio/).
3. Click on "Tools" from the RStudio menu and then select "Install Packages..." to bring up the "Install Packages" dialog box.
4. From the dialog box, select "Package Archive File (.zip; .tar.gz)" as the source from which to install, and browse to and select the downloaded package archive file.
5. Install packages `ggplot2`, `gtools`, and `pROC` from the CRAN selection in the dialog box if you have not installed these packages previously.  Alternatively, these can be installed from the R console with the command.

```{r eval = FALSE}
install.packages(c("ggplot2", "gtools", "pROC"))
```

| Operating System      | Package Archive File | 
|-----------------------|----------------------|
| Microsoft Windows: | [MRMCaov_0.1.4.zip](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/EdvySJhOuwhJiZFeuczm1AgBNAnv9GIEYeqxkl3u42UI3g) |
| Non-Windows: | [MRMCaov_0.1.4.tar.gz](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/EUU-MZ2Rk-1PjqQeg7OTFiwB_0XSUg_lKtdqAdp0bp5vnQ) |


## Getting Started

```{r mrmc, message=FALSE}
## Load the package
library(MRMCaov)

## View main help page
?mrmc

## Analyze the VanDyke dataset
est <- mrmc(empirical_auc(truth, rating), treatment, reader, case, data = VanDyke)
plot(est)
summary(est)
```
