---
title: "MRMCaov: Multi-Reader Multi-Case Analysis of Variance"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

**MRMCaov** is an R package for statistical comparison of diagnostic tests - such as those based on medical imaging - for which ratings have been obtained from multiple readers and on multiple cases.  Features of the package include the following.

* Performance metrics: area under the receiver operating characteristic curve (empirical/trapezoidal and proper parametric curves)
* Study designs: factorial, cases nested within readers, cases nested within tests, partially-paired cases
* Covariance estimation methods: DeLong, jackknife, unbiased


## Download and Installation

To install the package, download the archive file for your operating system from the links provided in the table below.  Next, do the following:

1. Run [RStudio](https://www.rstudio.com/products/rstudio/).
2. Click on "Tools" from the RStudio menu and then select "Install Packages..." to bring up the "Install Packages" dialog box.
3. From the dialog box, select "Package Archive File (.zip; .tar.gz)" as the source from which to install, and browse to and select the downloaded package archive file.

| Operating System      | Package Archive File | 
|-----------------------|----------------------|
| Microsoft Windows: | [MRMCaov_0.1.2.zip](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/EZlO1rYXXZ9HiT4fD4Q5AF8B-tyJQw087MlMfbsp-4nZEQ?e=mvIZPk) |
| Non-Windows: | [MRMCaov_0.1.2.tar.gz](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/EVvhUJr9mxJNixFiQVvFx8oB11kISQDxWz_Ay4gIPWb1nw?e=ZmIlUf) |


## Getting Started

```{r mrmc, message=FALSE}
## Load the package
library(MRMCaov)

## View main help page
?mrmc

## Analyze the VanDyke dataset
est <- mrmc(empirical_auc(truth, rating), treatment, reader, case, data = VanDyke)
plot(est)
summary(est)
```
