# Getting Started

**MRMCaov** is an R package for statistical comparison of diagnostic tests - such as those based on medical imaging - for which ratings have been obtained from multiple readers and on multiple cases.  Features of the package include the following.

* Statistical comparisons of diagnostic tests with respect to reader performance metrics
* Comparisons based on the ANOVA model of Obuchowski-Rockette and the unified framework of Hillis
* Reader performance metrics for area under receiver operating characteristic curves (ROC AUCs), partial AUCs, expected utility of ROC curves, likelihood ratio of positive or negative tests, sensitivity, specificity, and user-defined metrics
* Parametric and nonparametric estimation and plotting of ROC curves
* Support for factorial, nested, and partially paired study designs
* Inference for random or fixed readers and cases
* Conversion of Obuchowski-Rockette to Roe, Metz & Hillis model parameters and vice versa
* DeLong, jackknife, and unbiased covariance estimation
* Compatibility with Microsoft Windows, MacOS, and Linux

## Documentation: [User Guide](https://brian-j-smith.github.io/MRMCaov/using.html)

## Installation

Enter the following at the R console to install the package.

```{r eval = FALSE}
install.packages("MRMCaov")
```


## Citing the Software

```{r citation, comment = ""}
## Text format
citation("MRMCaov")

## Bibtex format
toBibtex(citation("MRMCaov"))
```
