## Description

**MRMCaov** is an R package for statistical comparison of diagnostic tests - such as those based on medical imaging - for which ratings have been obtained from multiple readers and on multiple cases.  Features of the package include the following.

* Comparison of imaging modalities or diagnostic tests with respect to ROC metrics
* ROC metrics include AUC, partial AUC, sensitivity, and specificity as well as user-defined metrics
* Parametric and nonparametric estimation and plotting of ROC curves
* Support for factorial and nested study designs
* DeLong, jackknife, and unbiased covariance estimation
* Inference for random or fixed readers and cases
* Compatibility with Microsoft Windows, Mac OS, and Linux


## Download and Installation

To install the package, do the following:

1. Download the archive file for your operating system from the links provided in the table below.
2. Run [RStudio](https://www.rstudio.com/products/rstudio/).
3. Click on "Tools" from the RStudio menu and then select "Install Packages..." to bring up the "Install Packages" dialog box.
4. From the dialog box, select "Package Archive File (.zip; .tar.gz)" as the source from which to install, and browse to and select the downloaded package archive file.
5. Install the packages below with the given command submitted at the R console, if they have not been installed previously.

```{r eval = FALSE}
install.packages(c("ggplot2", "gtools", "mvtnorm", "pROC", "tibble"))
```

| Operating System      | Package Archive File | 
|-----------------------|----------------------|
| Microsoft Windows: | [MRMCaov_0.1.13.zip](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/Ebpgd5dMPg5Gis5PDX7Ic3AB9Ele-lEi7d9jjsBylBTXqg) |
| Linux: | [MRMCaov_0.1.13.tar.gz](https://iowa-my.sharepoint.com/:u:/g/personal/bjsmith_uiowa_edu/ESWlswNxJClKmdVX5e9ncvoB_e643njNgLFL5FhAKkT6Cw) |


## Citing the Software

```{r citation, comment = ""}
## Text format
citation("MRMCaov")

## Bibtex format
toBibtex(citation("MRMCaov"))
```
