# Single-Reader Multi-Case Analysis

A single-reader multi-case (SRMC) analysis involves a single readers of multiple cases to compare reader performance metrics across two or more diagnostic tests.  An SRMC analysis can be performed with a call to `srmc()`.

> **SRMC Function**
>
> `srmc(response, test, case, data, cov = jackknife)`
>
> *Description*
>
> Returns an `srmc` class object of data that can be used to estimate and compare reader performance metrics in a single-reader multi-case statistical analysis.
>
> *Arguments*
>
> * `response`: object defining true case statuses, corresponding reader ratings, and a reader performance metric to compute on them.
> * `test`, `case`: variables containing the test and case identifiers for the `response` observations.
> * `data`: data frame containing the response and identifier variables.
> * `cov`: function `jackknife`, `unbiased`, or `DeLong` to estimate reader performance metric covariances.

The function is used similar to `mrmc()` but without the `reader` argument.  Below is an example SRMC analysis performed with one of the readers from the `VanDyke` dataset.

```{r using_srmc_roc}
## Subset VanDyke dataset by reader 1
VanDyke1 <- subset(VanDyke, reader == "1")

## Compare ROC AUC treatment means for reader 1
est <- srmc(binormal_auc(truth, rating), treatment, case, data = VanDyke1)
```

<details>
<summary>**Show SRMC Performance Metrics**</summary>
```{r}
print(est)
```
</details>
<details>
<summary>**Show SRMC ROC Curves**</summary>
```{r}
plot(est)
```
</details>
<details>
<summary>**Show SRMC ROC Curve Parameters**</summary>
```{r}
print(parameters(est))
```
</details>
<details>
<summary>**Show SRMC Test Results**</summary>
```{r}
summary(est)
```
</details>
<p>
