# Single-Test Multi-Case Analysis

A single-test and single-reader multi-case (STMC) analysis involves a single reader of multiple cases to estimate a reader performance metric for one diagnostic test.  An STMC analysis can be performed with a call to `stmc()`.

> **STMC Function**
>
> `stmc(response, case, data, cov = jackknife)`
>
> *Description*
>
> Returns an `stmc` class object of data that can be used to estimate a reader performance metric in a single-test and single-reader multi-case statistical analysis.
>
> *Arguments*
>
> * `response`: object defining true case statuses, corresponding reader ratings, and a reader performance metric to compute on them.
> * `case`: variable containing the case identifiers for the `response` observations.
> * `data`: data frame containing the response and identifier variables.
> * `cov`: function `jackknife`, `unbiased`, or `DeLong` to estimate reader performance metric covariances.

The function is used similar to `mrmc()` but without the `test` and `reader` arguments.  In the following example, an STMC analysis is performed with one of the tests and readers from the `VanDyke` dataset.

```{r using_trmc_roc}
## Subset VanDyke dataset by treatment 1 and reader 1
VanDyke11 <- subset(VanDyke, treatment == "1" & reader == "1")

## Estimate ROC AUC for treatment 1 and reader 1
est <- stmc(binormal_auc(truth, rating), case, data = VanDyke11)
```

<details>
<summary>**Show STMC ROC Curve**</summary>
```{r}
plot(est)
```
</details>
<details>
<summary>**Show STMC ROC Curve Parameters**</summary>
```{r}
print(parameters(est))
```
</details>
<details>
<summary>**Show STMC ROC AUC Estimate**</summary>
```{r}
summary(est)
```
</details>
<p>
