# Single-Reader Multi-Case Analysis

A single-reader multi-case (SRMC) analysis involves a single readers of multiple cases to compare reader performance metrics across two or more diagnostic tests.  An SRMC analysis can be performed with a call to `srmc()`.

\begin{figure}[h]
\begin{tcolorbox}[title=SRMC Function]
\textbf{Syntax}
\begin{verbatim}
srmc(response, test, case, data, cov = jackknife
\end{verbatim}
\begin{Description}
Returns an \code{srmc} class object of data that can be used to estimate and compare reader performance metrics in a single-reader multi-case statistical analysis.
\end{Description}
\textbf{Arguments}
\begin{description}
\item[\code{response}:] object defining true case statuses, corresponding reader ratings, and a reader performance metric to compute on them.
\item[\code{test}, \code{case}:] variables containing the test and case identifiers for the \code{response} observations.
\item[\code{data}:] data frame containing the response and identifier variables.
\item[\code{cov}:] function \code{jackknife}, \code{unbiased}, or \code{DeLong} to estimate reader performance metric covariances.
\end{description}
\end{tcolorbox}
\end{figure}

The function is used similar to `mrmc()` but without the `reader` argument.  Below is an example SRMC analysis performed with one of the readers from the `VanDyke` dataset.

```{r using_srmc_roc}
## Subset VanDyke dataset by reader 1
VanDyke1 <- subset(VanDyke, reader == "1")

## Compare ROC AUC treatment means for reader 1
est <- srmc(binormal_auc(truth, rating), treatment, case, data = VanDyke1)
```

**SRMC Performance Metrics**

```{r}
print(est)
```

**SRMC ROC Curves**

```{r}
plot(est)
```

**SRMC ROC Curve Parameters**

```{r}
print(parameters(est))
```

**SRMC Test Results**

```{r}
summary(est)
```
