# Single-Test Multi-Case Analysis

A single-test and single-reader multi-case (STMC) analysis involves a single reader of multiple cases to estimate a reader performance metric for one diagnostic test.  An STMC analysis can be performed with a call to `stmc()`.

\begin{figure}[h]
\begin{tcolorbox}[title=STMC Function]
\textbf{Syntax}
\begin{verbatim}
stmc(response, case, data, cov = jackknife)
\end{verbatim}
\begin{Description}
Returns an \code{stmc} class object of data that can be used to estimate a reader performance metric in a single-test and single-reader multi-case statistical analysis.
\end{Description}
\textbf{Arguments}
\begin{description}
\item[\code{response}:] object defining true case statuses, corresponding reader ratings, and a reader performance metric to compute on them.
\item[\code{case}:] variable containing the case identifiers for the \code{response} observations.
\item[\code{data}:] data frame containing the response and identifier variables.
\item[\code{cov}:] function \code{jackknife}, \code{unbiased}, or \code{DeLong} to estimate reader performance metric covariances.
\end{description}
\end{tcolorbox}
\end{figure}

The function is used similar to `mrmc()` but without the `test` and `reader` arguments.  In the following example, an STMC analysis is performed with one of the tests and readers from the `VanDyke` dataset.

```{r using_trmc_roc}
## Subset VanDyke dataset by treatment 1 and reader 1
VanDyke11 <- subset(VanDyke, treatment == "1" & reader == "1")

## Estimate ROC AUC for treatment 1 and reader 1
est <- stmc(binormal_auc(truth, rating), case, data = VanDyke11)
```

**STMC ROC Curve**

```{r}
plot(est)
```

**STMC ROC Curve Parameters**

```{r}
print(parameters(est))
```

**STMC ROC AUC Estimate**

```{r}
summary(est)
```
